---
title: "Modeling"
output: html_document
---
```{r}
library(readr)
library(dplyr)
library(ggplot2)

AllGames2019 <- read_csv("~/March Madness/AllGames2019.csv")
final.df <- read_csv("~/March Madness/Final.csv") %>%
  mutate(ORtg_diff = ORtg-ORtg_Opp, DRtg_diff = DRtg-DRtg_Opp, rate = (ORtg-DRtg_Opp)-(ORtg_Opp-DRtg), ast_tov_tot = AST_tot/TOV_tot, ast_tov_opp = AST_Opp/TOV_Opp, ast_tov_diff = ast_tov_tot-ast_tov_opp, AST_Diff = AST_tot-AST_Opp, `FG%_Diff`=`FG%_tot`-`FG%_Opp`, STL_diff = STL_tot-STL_Opp, BLK_diff = BLK_tot -BLK_Opp, TOV_diff = TOV_tot-TOV_Opp, Pace_diff= Pace-Pace_Opp, SOS_diff = SOS-SOS_Opp, SRS_diff = SRS-SRS_Opp)

temp <- final.df %>%
  select(ORtg, ORtg_Opp, DRtg, DRtg_Opp, ORtg_diff, DRtg_diff, rate, Win)

grouped <- AllGames2019 %>%
  group_by(Team) %>%
  summarize(Off =mean(Off_Eff), Def =mean(Def_Eff), Opp_Off=mean(Opp_Off_Eff), Opp_Def=mean(Opp_Def_Eff)) %>%
  mutate(diff=Off-Def)

```

Look at variables:

ORtg, ORtg_Opp, AST%, AST%_Opp, Pace, TOV_tot, 

Opponent offense - defensive
Your offense - opponent defensive

(TO-OD)/(TD-OO)


```{r}
mod1 <- glm(`Win` ~ rate, data = final.df, family = "binomial")
summary(mod1) #rate not significant

mod2 <- glm(`Win` ~ ORtg_diff+DRtg_diff, data = final.df, family = "binomial")
summary(mod2)

mod3 <- glm(`Win` ~ ORtg_diff+DRtg_diff+ast_tov_tot+ast_tov_opp, data = final.df, family = "binomial")
summary(mod3) #Ast/tov not significant

mod4 <- glm(`Win` ~ ORtg_diff+DRtg_diff+AST_Diff, data = final.df, family = "binomial")
summary(mod4) #AST not significant

mod5 <- glm(`Win` ~ ORtg_diff+DRtg_diff+`FG%_Diff`, data = final.df, family = "binomial")
summary(mod5) #FG%_difference is significant


mod6 <- glm(`Win` ~ ORtg_diff+DRtg_diff+`FG%_Diff`+STL_diff, data = final.df, family = "binomial")
summary(mod6) #Steals not significant

mod7 <- glm(`Win` ~ ORtg_diff+DRtg_diff+`FG%_Diff`+BLK_diff, data = final.df, family = "binomial")
summary(mod7) #Blocks are significant

mod8 <- glm(`Win` ~ ORtg_diff+DRtg_diff+`FG%_Diff`+BLK_diff+`FT%_tot`, data = final.df, family = "binomial")
summary(mod8) #FT not significant

mod9 <- glm(`Win` ~ ORtg_diff+DRtg_diff+`FG%_Diff`+BLK_diff+`3P%_tot`, data = final.df, family = "binomial")
summary(mod9) #3P not significant

mod10 <- glm(`Win` ~ ORtg_diff+DRtg_diff+`FG%_Diff`+BLK_diff+`TOV_diff`, data = final.df, family = "binomial")
summary(mod10) #TOV_diff not significant

mod11 <- glm(`Win` ~ ORtg_diff+DRtg_diff+`FG%_Diff`+BLK_diff+Pace_diff, data = final.df, family = "binomial")
summary(mod11) #Pace is not significant

mod12 <- glm(`Win` ~ ORtg_diff+DRtg_diff+`FG%_Diff`+BLK_diff+SOS, data = final.df, family = "binomial")
summary(mod12) #Strength of Schedule is significant!

mod13 <- glm(`Win` ~ ORtg_diff+DRtg_diff+`FG%_Diff`+BLK_diff+SOS+SRS, data = final.df, family = "binomial")
summary(mod13) #Strength of Schedule is significant!

###
# Remmove FG%_Diff because of collinearity
###
mod14 <- glm(`Win` ~ ORtg_diff+DRtg_diff+BLK_diff+SOS, data = final.df, family = "binomial")
summary(mod14) #Strength of Schedule is significant!

mod15 <- glm(`Win` ~ ORtg_diff+DRtg_diff+BLK_diff+SRS, data = final.df, family = "binomial")
summary(mod15) #SRS is significant!

vif(mod15)

mod16 <- glm(`Win` ~ ORtg_diff+DRtg_diff+BLK_diff+SRS+SOS, data = final.df, family = "binomial")
summary(mod16) #SRS is significant!
vif(mod16) #Collinearity between SRS and SOS

mod17 <- glm(`Win` ~ ORtg_diff+DRtg_diff+SOS+SOS_Opp, data = final.df, family = "binomial")
summary(mod17) #SRS is significant!
vif(mod17) #Collinearity between SOS and SOS_Opp

mod18 <- glm(`Win` ~ ORtg_diff+DRtg_diff+SOS_diff, data = final.df, family = "binomial")
summary(mod18) #SRS is significant!
vif(mod18) #Collinearity between SOS and SOS_Opp
```


Model 18 seems to be the best.

Exponentiated Coefficients and Confidence Interval 
```{r}
exp(cbind(OR = coef(mod18), confint(mod18)))
```

Prediction
```{r}
probs <- predict(mod18,data=final.df,type="response")
head(probs)
log.odds<- predict(mod18,data=final.df)
probs0<- exp(log.odds)/(1+exp(log.odds))
head(cbind(probs,probs0))
final.df <- mutate(final.df,prob.log = probs)


```

Training vs Testing with 4 predictors
```{r}
(n<-nrow(final.df))

errs <- numeric(20)
tval <- numeric(20)

calcErr <- function(thresh.default) {
 test.df<-test.df %>% 
  mutate(games.pred= ifelse(prob.log< thresh.default,0,1))
  with(test.df,mean(Win!=games.pred))
}

for(i in 1:20){
  train<-sample(1:n,n/2,rep=F)
  train.df<-final.df[train,]
  test.df<-final.df[-train,]
  mod.log <- glm(`Win` ~ ORtg_diff+DRtg_diff+BLK_diff+SOS_diff, data = train.df, family = "binomial")
  summary(mod.log)
  probs <- predict(mod.log,newdata=test.df,type="response")
  test.df <- mutate(test.df,prob.log = probs)
  threshVals<-.5
  err.preds<-map_dbl(threshVals,calcErr)
  min(err.preds)
  id.min<-which.min(err.preds)
  threshVals[id.min]

  errs[i]=  min(err.preds)
  tval[i]=threshVals[id.min]
}

cbind(errs, tval)
mean(errs)
mean(tval)
```

Training vs Testing with 3 predictors
```{r}
(n<-nrow(final.df))

errs <- numeric(20)
tval <- numeric(20)

calcErr <- function(thresh.default) {
 test.df<-test.df %>% 
  mutate(games.pred= ifelse(prob.log< thresh.default,0,1))
  with(test.df,mean(Win!=games.pred))
}

for(i in 1:20){
  train<-sample(1:n,n/2,rep=F)
  train.df<-final.df[train,]
  test.df<-final.df[-train,]
    mod.log <- glm(`Win` ~ ORtg_diff+DRtg_diff+SOS_diff, data = train.df, family = "binomial")
  summary(mod.log)
  probs <- predict(mod.log,newdata=test.df,type="response")
  test.df <- mutate(test.df,prob.log = probs)
  threshVals<-.5
  err.preds<-map_dbl(threshVals,calcErr)
  min(err.preds)
  id.min<-which.min(err.preds)
  threshVals[id.min]

  errs[i]=  min(err.preds)
  tval[i]=threshVals[id.min]
}

cbind(errs, tval)
mean(errs)
mean(tval)
```

3 Predictors is better than 4

Training vs Testing with 2 predictors
```{r}
(n<-nrow(final.df))

errs <- numeric(20)
tval <- numeric(20)

calcErr <- function(thresh.default) {
 test.df<-test.df %>% 
  mutate(games.pred= ifelse(prob.log< thresh.default,0,1))
  with(test.df,mean(Win!=games.pred))
}

for(i in 1:20){
  train<-sample(1:n,n/2,rep=F)
  train.df<-final.df[train,]
  test.df<-final.df[-train,]
  mod.log <- glm(`Win` ~ ORtg_diff+DRtg_diff, data = train.df, family = "binomial")
  probs <- predict(mod.log,newdata=test.df,type="response")
  test.df <- mutate(test.df,prob.log = probs)
  threshVals<-.5
  err.preds<-map_dbl(threshVals,calcErr)
  min(err.preds)
  id.min<-which.min(err.preds)
  threshVals[id.min]

  errs[i]=  min(err.preds)
  tval[i]=threshVals[id.min]
}

cbind(errs, tval)
mean(errs)
mean(tval)
```

Using 3 predictors is the best
```{r}
library(car)
mod.log3_preds <- glm(`Win` ~ ORtg_diff+DRtg_diff+SOS_diff, data = final.df, family = "binomial")

vif(mod.log3_preds)
```



```{r}
calcErr <- function(thresh.default) {
 final.df<-final.df %>% 
  mutate(games.pred= ifelse(prob.log< thresh.default,0,1))
  with(final.df,mean(Win!=games.pred))
}
  
thresh.pred <-.5

final.df<-final.df %>% 
  mutate(pred.log= ifelse(prob.log < thresh.pred ,0,1))

final.df %>%
  count(pred.log)

with(final.df,table(Win, pred.log))

(err.log <- with(final.df, mean(Win != pred.log)))

final.df %>%
    group_by(Team)%>%
    summarize(err=mean(!Win == pred.log),
              err.null=mean(`W/L`=="W"),
              err.ratio=err/err.null)


```


