---
title: "Predictions"
output: html_document
---

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)

AllGames2019 <- read_csv("~/March Madness/AllGames2019.csv")
final.df <- read_csv("~/March Madness/Final.csv") %>%
  mutate(ORtg_diff = ORtg-ORtg_Opp, DRtg_diff = DRtg-DRtg_Opp, rate = (ORtg-DRtg_Opp)-(ORtg_Opp-DRtg), ast_tov_tot = AST_tot/TOV_tot, ast_tov_opp = AST_Opp/TOV_Opp, ast_tov_diff = ast_tov_tot-ast_tov_opp, AST_Diff = AST_tot-AST_Opp, `FG%_Diff`=`FG%_tot`-`FG%_Opp`, STL_diff = STL_tot-STL_Opp, BLK_diff = BLK_tot -BLK_Opp, TOV_diff = TOV_tot-TOV_Opp, Pace_diff= Pace-Pace_Opp, SOS_diff = SOS-SOS_Opp, SRS_diff = SRS-SRS_Opp)

temp <- final.df %>%
  select(ORtg, ORtg_Opp, DRtg, DRtg_Opp, ORtg_diff, DRtg_diff, rate, Win)

grouped <- AllGames2019 %>%
  group_by(Team) %>%
  summarize(Off =mean(Off_Eff), Def =mean(Def_Eff), Opp_Off=mean(Opp_Off_Eff), Opp_Def=mean(Opp_Def_Eff)) %>%
  mutate(diff=Off-Def)

mod_pred <- glm(`Win` ~ ORtg_diff+DRtg_diff+SOS_diff, data = final.df, family = "binomial")
summary(mod_pred) #Strength of Schedule is significant!



```

```{r}
logit2prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}
```

# Duke vs North Dakota State: Duke

```{r}
team1 <- read_csv("~/March Madness/team1.csv")

team <- team1 %>%
  filter(School=="Duke" | School=="North Dakota State")
head(team)

(intercept <- coef(mod_pred)[1])
(ORtg_diff <- coef(mod_pred)[2])
(DRtg_diff <- coef(mod_pred)[3])
(SOS_diff <- coef(mod_pred)[4])

(logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS))

logit2prob(logits)


```

# VCU vs UCF: UCF

```{r}
team <- team1 %>%
  filter(School=="VCU" | School=="UCF")
head(team)

(intercept <- coef(mod_pred)[1])
(ORtg_diff <- coef(mod_pred)[2])
(DRtg_diff <- coef(mod_pred)[3])
(SOS_diff <- coef(mod_pred)[4])

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))


```

# Mississippi State vs Liberty: Mississippi State

```{r}
team <- team1 %>%
  filter(School=="Mississippi State" | School=="Liberty")
head(team)

(intercept <- coef(mod_pred)[1])
(ORtg_diff <- coef(mod_pred)[2])
(DRtg_diff <- coef(mod_pred)[3])
(SOS_diff <- coef(mod_pred)[4])

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Virginia Tech vs Saint Louis: Virginia Tech

```{r}
team <- team1 %>%
  filter(School=="Virginia Tech" | School=="Saint Louis")
head(team)

(intercept <- coef(mod_pred)[1])
(ORtg_diff <- coef(mod_pred)[2])
(DRtg_diff <- coef(mod_pred)[3])
(SOS_diff <- coef(mod_pred)[4])

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))

```

# Maryland vs Belmont: Maryland

```{r}
team <- team1 %>%
  filter(School=="Maryland" | School=="Belmont")
head(team)
(intercept <- coef(mod_pred)[1])
(ORtg_diff <- coef(mod_pred)[2])
(DRtg_diff <- coef(mod_pred)[3])
(SOS_diff <- coef(mod_pred)[4])

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))

```

# LSU vs Yale: LSU

```{r}
team <- team1 %>%
  filter(School=="LSU" | School=="Yale")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))

```

# Louisville vs Minnesota: Louisville

```{r}
team <- team1 %>%
  filter(School=="Louisville" | School=="Minnesota")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))

```


# Michigan State vs Bradley: Michigan State

```{r}
team <- team1 %>%
  filter(School=="Michigan State" | School=="Bradley")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))

```

# Gonzaga vs Fairleigh: Gonzaga

```{r}
team <- team1 %>%
  filter(School=="Gonzaga" | School=="Fairleigh")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))

```

# Syracuse vs Baylor: Baylor

```{r}
team <- team1 %>%
  filter(School=="Syracuse" | School=="Baylor")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Marquette vs Murray State: Marquette

```{r}
team <- team1 %>%
  filter(School=="Marquette" | School=="Murray State")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# FSU vs Vermont: FSU

```{r}
team <- team1 %>%
  filter(School=="FSU" | School=="Vermont")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))

```

# Buffalo vs Arizona State: Arizona State

```{r}
team <- team1 %>%
  filter(School=="Buffalo" | School=="Arizona State")
head(team)


logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Texas Tech vs Northern Kentucky: Texas Tech

```{r}
team <- team1 %>%
  filter(School=="Texas Tech" | School=="Northern Kentucky")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Nevada vs Florida: Florida

```{r}
team <- team1 %>%
  filter(School=="Nevada" | School=="Florida")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```


# Virginia vs Gardner-Webb: Virginia

```{r}
team <- team1 %>%
  filter(School=="Virginia" | School=="Gardner-Webb")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Oklahoma vs Ole Miss: Ole Miss

```{r}
team <- team1 %>%
  filter(School=="Oklahoma" | School=="Ole Miss")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Oregon vs Wisconsin: Wisconsin

```{r}
team <- team1 %>%
  filter(School=="Oregon" | School=="Wisconsin")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Kansas State vs UC-Irvine: Kansas State

```{r}
team <- team1 %>%
  filter(School=="Kansas State" | School=="UC-Irvine")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Villanova vs Saint Mary's: Villanova

```{r}
team <- team1 %>%
  filter(School=="Villanova" | School=="Saint Mary's")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Purdue vs Old Dominion: Purdue

```{r}
team <- team1 %>%
  filter(School=="Purdue" | School=="Old Dominion")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Cincinnati vs Iowa: Iowa

```{r}
team <- team1 %>%
  filter(School=="Cincinnati" | School=="Iowa")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Tennessee vs Colgate: Tennessee

```{r}
team <- team1 %>%
  filter(School=="Tennessee" | School=="Colgate")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# UNC vs Iona: UNC

```{r}
team <- team1 %>%
  filter(School=="UNC" | School=="Iona")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Utah State vs Washington: Washington

```{r}
team <- team1 %>%
  filter(School=="Utah State" | School=="Washington")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Auburn vs New Mexico State: Auburn

```{r}
team <- team1 %>%
  filter(School=="Auburn" | School=="New Mexico State")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Kansas vs Northeastern: Kansas

```{r}
team <- team1 %>%
  filter(School=="Kansas" | School=="Northeastern")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Iowa State vs Ohio State: Iowa State

```{r}
team <- team1 %>%
  filter(School=="Iowa State" | School=="Ohio State")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Houston vs Georgia State: Georgia State

```{r}
team <- team1 %>%
  filter(School=="Houston" | School=="Georgia State")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Wofford vs Seton Hall: Seton Hall

```{r}
team <- team1 %>%
  filter(School=="Wofford" | School=="Seton Hall")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Kentucky vs Abil Christian: Kentucky

```{r}
team <- team1 %>%
  filter(School=="Kentucky" | School=="Abilene Christian")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```


# Round 2

# Duke vs UCF: Kentucky

```{r}
team <- team1 %>%
  filter(School=="Duke" | School=="UCF")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Mississippi State vs Virginia Tech: Mississippi State

```{r}
team <- team1 %>%
  filter(School=="Mississippi State" | School=="Virginia Tech")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Maryland vs LSU: LSU

```{r}
team <- team1 %>%
  filter(School=="Maryland" | School=="LSU")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Louisville vs Michigan State: Michigan State

```{r}
team <- team1 %>%
  filter(School=="Michigan State" | School=="Louisville")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Gonzaga vs Baylor: Michigan State

```{r}
team <- team1 %>%
  filter(School=="Baylor" | School=="Gonzaga")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Marquette vs Florida State: Florida State

```{r}
team <- team1 %>%
  filter(School=="Marquette" | School=="FSU")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Arizona State vs Buffalo: Arizona State

```{r}
team <- team1 %>%
  filter(School=="Arizona State" | School=="Texas Tech")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Michigan vs Florida: Florida

```{r}
team <- team1 %>%
  filter(School=="Michigan" | School=="Florida")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Virginia vs Ole Miss: Ole Miss

```{r}
team <- team1 %>%
  filter(School=="Virginia" | School=="Ole Miss")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Wisconsin vs Kansas State: Wisconsin

```{r}
team <- team1 %>%
  filter(School=="Wisconsin" | School=="Kansas State")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Villanova vs Purdue: Purdue

```{r}
team <- team1 %>%
  filter(School=="Villanova" | School=="Purdue")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Tennessee vs Iowa: Iowa

```{r}
team <- team1 %>%
  filter(School=="Tennessee" | School=="Iowa")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# UNC vs Washington: UNC

```{r}
team <- team1 %>%
  filter(School=="UNC" | School=="Washington")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Auburn vs Kansas: Auburn

```{r}
team <- team1 %>%
  filter(School=="Auburn" | School=="Kansas")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Iowa State vs Georgia State: Iowa State

```{r}
team <- team1 %>%
  filter(School=="Iowa State" | School=="Georgia State")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Kentucky vs Seton Hall: Kentucky

```{r}
team <- team1 %>%
  filter(School=="Kentucky" | School=="Seton Hall")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Round 3

# Duke vs Mississippi
```{r}
team <- team1 %>%
  filter(School=="Duke" | School=="Mississippi State")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# LSU vs Michigan State: Michigan State
```{r}
team <- team1 %>%
  filter(School=="LSU" | School=="Michigan State")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Gonzaga vs Florida State: Gonzaga
```{r}
team <- team1 %>%
  filter(School=="Gonzaga" | School=="FSU")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Arizona State vs Florida: Florida
```{r}
team <- team1 %>%
  filter(School=="Arizona State" | School=="Florida")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Ole Miss vs Wisconsin: Ole Miss
```{r}
team <- team1 %>%
  filter(School=="Ole Miss" | School=="Wisconsin")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Purdue vs Iowa: Purdue
```{r}
team <- team1 %>%
  filter(School=="Purdue" | School=="Iowa")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# UNC vs Auburn: UNC
```{r}
team <- team1 %>%
  filter(School=="UNC" | School=="Auburn")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Iowa State vs Kentucky: Iowa State
```{r}
team <- team1 %>%
  filter(School=="Iowa State" | School=="Kentucky")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Mississippi State vs Michigan State: Michigan
```{r}
team <- team1 %>%
  filter(School=="Mississippi State" | School=="Michigan State")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Gonzaga vs Florida: Gonzaga
```{r}
team <- team1 %>%
  filter(School=="Gonzaga" | School=="Florida")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Ole Miss vs Purdue: Purdue
```{r}
team <- team1 %>%
  filter(School=="Ole Miss" | School=="Purdue")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# UNC vs Iowa State: Purdue
```{r}
team <- team1 %>%
  filter(School=="UNC" | School=="Iowa State")
head(team)

logits <- intercept+ORtg_diff*(team[2,]$ORtg-team[1,]$ORtg)-DRtg_diff*(team[2,]$DRtg-team[1,]$DRtg)+SOS_diff*(team[2,]$SOS-team[1,]$SOS)

(logit2prob(logits))
```

# Round 4

# Michigan State vs Gonzaga: Michigan State
```{r}
team <- team1 %>%
  filter(School=="Michigan State" | School=="Gonzaga")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# UNC vs Purdue: Purdue
```{r}
team <- team1 %>%
  filter(School=="UNC" | School=="Purdue")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

# Round 5

# Michigan State vs Purdue: Purdue
```{r}
team <- team1 %>%
  filter(School=="Michigan State" | School=="Purdue")
head(team)

logits <- intercept+ORtg_diff*(team[1,]$ORtg-team[2,]$ORtg)-DRtg_diff*(team[1,]$DRtg-team[2,]$DRtg)+SOS_diff*(team[1,]$SOS-team[2,]$SOS)

(logit2prob(logits))
```

```{r}
team1 %>%
  count(School)
```

